Real Time Variational Density Forecasts

### 2017-02-20 Confirmation/confirmation_V2.tex
reference fixes

In the event that (\ref{mf2}) is from an unrecognisable distribution a further approximation can be used, substituting in another distribution for the problematic $q_i(\theta_i |\boldsymbol{\lambda_i}).$ One method in \citet{Friston2006} uses a Laplace approximation for these unrecognizable $q_i(\theta_i |\boldsymbol{\lambda_i})$ by matching the mode and inverse hessian matrix to a gaussian distribution, though the only requirement is that the substitute has an expectation that is a tractable function of its parameters to be used for other parameters in (\ref{mf2}).

@@

Given a sample of $\boldsymbol{\theta}$, \citet{Dssmann2013} provide an algorithm to select the best vine factorisation by maximising Kendall's Tau, and the best family for each bivariate copula by minimising an information criterion such as AIC. In the real-time forecasting models used for electricity load demand, MCMC samples of the posterior distribution are available, though often immediately out of date. The approach used in this thesis is to run an MCMC algorithm, thin the resulting draws until they are effectively independent, choose an optimal family for each marginal distribution by AIC, then run (Vine copula algorithm here) to infer an optimal vine copula. This results in an approximating distribution $q(\boldsymbol{\theta} | \boldsymbol{\lambda})$ that can then be used in an SVB algorithm to update $q(\boldsymbol{\theta} | \boldsymbol{\lambda})$ as more observations become available. MCMC can be ran simultaenously and the resulting sample can be used to check if the distribution $q$ should be changed.

>>>>

In the event that (\ref{mf2}) is from an unrecognisable distribution a further approximation can be used, substituting in another distribution for the problematic $q_i(\theta_i |\boldsymbol{\lambda_i}).$ \citet{Friston2006} and \citet{Wang2013} suggests the use of a Gaussian distribution through either a Laplace approximation or a Delta Method transform, though the only requirement is that the substitute distribution has an expectation that is a tractable function of its parameters to be used for other parameters in (\ref{mf2}).

@@

Given a sample of $\boldsymbol{\theta}$, \citet{Dissmann2013} provide an algorithm to select the best vine factorisation by maximising Kendall's Tau, and the best family for each bivariate copula by minimising an information criterion such as AIC. In the real-time forecasting models used for electricity load demand, MCMC samples of the posterior distribution are available, though often immediately out of date. The approach used in this thesis is to run an MCMC algorithm, thin the resulting draws until they are effectively independent, choose an optimal family for each marginal distribution by AIC, then run (Vine copula algorithm here) to infer an optimal vine copula. This results in an approximating distribution $q(\boldsymbol{\theta} | \boldsymbol{\lambda})$ that can then be used in an SVB algorithm to update $q(\boldsymbol{\theta} | \boldsymbol{\lambda})$ as more observations become available. MCMC can be ran simultaenously and the resulting sample can be used to check if the distribution $q$ should be changed.
